Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
grammar: separate sentences by . not ,

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier work. To get a measure for the
classifier's accuracy we retrain it in a cross-validation scheme, this
yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}

>>>>

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier work. To get a measure for the
classifier's accuracy we retrain it in a cross-validation scheme.
This yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}
